Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-05-21 manuscript/manuscript.Rmd
updates Table 1

@@

colnames(stats_table) <- c("Model", "Species", "MAE", "Accuracy", "Mean Obs. Cover")
print.xtable(xtable(stats_table, caption = "Mean absolute error (MAE) and accuracy (Pearson's $\\rho$) for one-step-ahead forecast from both model types. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation"),type="latex", comment=FALSE, include.rownames=FALSE)
```

>>>>

mae_list <- list()
mae_pvals <- list()
species <- unique(qbmstats$species)
for(spp in species){
  tmp1 <- subset(tmpipm, species==spp)
  tmp2 <- subset(tmpqbm, species==spp)
  err1 <- as.data.frame(abs(tmp1$mean_obs - tmp1$mean_pred))
  err2 <- as.data.frame(abs(tmp2$mean_obs - tmp2$mean_pred))
  colnames(err1) <- "resid"
  err1$model <- "ipm"
  colnames(err2) <- "resid"
  err2$model <- "qbm"
  errd <-  rbind(err1, err2)
  mae_ttest <- with(errd, t.test(resid~model, alternative = "less"))
  mae_list[[spp]] <- mae_ttest
  mae_pvals[[spp]] <- mae_ttest[["p.value"]]
}

mae_ps <- melt(mae_pvals)

@@

colnames(stats_table) <- c("Species", "Model", "MAE", "Accuracy", "Mean Obs. Cover")
print.xtable(xtable(stats_table, caption = "Mean absolute error (MAE) and accuracy (Pearson's $\\rho$) for one-step-ahead forecast from both model types. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation."),type="latex", comment=FALSE, include.rownames=FALSE)
```

### 2015-05-21 manuscript/manuscript.tex
updates Table 1

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
Model & Species & MAE & Accuracy & Mean Obs. Cover \\ 
  \hline
IPM & BOGR & 4.77 & 0.90 & 9.16 \\ 
  QBM & BOGR & 5.30 & 0.88 & 9.22 \\ 
  IPM & HECO & 0.60 & 0.80 & 1.22 \\ 
  QBM & HECO & 2.03 & 0.84 & 1.25 \\ 
  IPM & PASM & 0.18 & 0.65 & 0.40 \\ 
  QBM & PASM & 0.17 & 0.87 & 0.40 \\ 
  IPM & POSE & 0.78 & 0.61 & 1.23 \\ 
  QBM & POSE & 1.30 & 0.57 & 1.25 \\ 
   \hline
\end{tabular}
\caption{Mean absolute error (MAE) and accuracy (Pearson's $\rho$) for one-step-ahead forecast from both model types. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation} 
\end{table}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
Species & Model & MAE & Accuracy & Mean Obs. Cover \\ 
  \hline
IPM & BOGR & 4.77 & 0.90 & 9.16 \\ 
  QBM & BOGR & 5.30 & 0.88 & 9.22 \\ 
  IPM & HECO & 0.60 & 0.80 & 1.22 \\ 
  QBM & HECO & 2.03 & 0.84 & 1.25 \\ 
  IPM & PASM & 0.18 & 0.65 & 0.40 \\ 
  QBM & PASM & 0.17 & 0.87 & 0.40 \\ 
  IPM & POSE & 0.78 & 0.61 & 1.23 \\ 
  QBM & POSE & 1.30 & 0.57 & 1.25 \\ 
   \hline
\end{tabular}
\caption{Mean absolute error (MAE) and accuracy (Pearson's $\rho$) for one-step-ahead forecast from both model types. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation.} 
\end{table}
